Citeopotamus

### 2012-12-07 paper/paper.tex
Committing my changes to the paper and then will merge Eriq's updated version.
Also changed the plos reference in refs.bib

\section{Introduction}\label{sec:introduction}
The problem of recommending citations for a technical paper is known and has many approaches to attempt to solve it.\cite{cite1,cite2,cite3,cite4,cite5,cite6,cite7,cite8} Solutions range from graph based social network approaches to language models to match meaning in both the paper and the recommended text. But the problem of recommending where inside the paper to put citations is unknown. 
The ideal solution would recommend an exact spot in the paper to put a specific citation. To solve this problem there exist two separate pieces. First, given a location of a citation the solution must be able to examine the references for the paper and choose the most appropriate citations.
Second, find locations where citations should go. We leave the second problem to be done in the future while we focus on solving the first in this paper.

@@

\section{Dataset}\label{sec:dataset}
%overview
%different components of the data
%implementation
%Metrics - #papers, #references, etc

>>>>

\section{Introduction}\label{sec:introduction}
The problem of recommending citations for a technical paper is known and has
many approaches to attempt to solve it~\cite{cite1, cite2, cite3, cite4, cite5,
cite6, cite7, cite8}. Solutions range from graph based social network
approaches to language models to match meaning in both the paper and the
recommended text. But the problem of recommending where inside the paper to put
citations is unknown.  The ideal solution would recommend an exact spot in the
paper to put a specific citation. To solve this problem there exist two
separate pieces. First, given a location of a citation the solution must be
able to examine the references for the paper and choose the most appropriate
citations.  Second, find locations where citations should go. We leave the
second problem to be done in the future while we focus on solving the first in
this paper.

@@

\section{Dataset}\label{sec:dataset}
%overview
The dataset for which we report results was collected from \textit{PLoS
Computational Biology}~\cite{plos}. PLoS (Public Library of Science) is a
nonprofit publisher that aims to accelerate progress in science. PLoS has
several journals--ONE, Biology, Medicine, Genetics, Computational Biology,
Pathogens, and Neglected Tropical Diseases--available to the public. For our
purposes we collected articles from PLoS Computational Biology, the
computational biology journal published by PLoS. We only collected articles
from this journal simply for the reason that as computer scientists it is the
most likely to be similar to computer science publications in style and in
content. We initially were interested in a corpus of computer science
publications, however we were unable to find a source that would allow us to
programmatically collect computer science publications and articles.

%different components of the data
From PLoS Computational Biology we collected a set of \textit{root papers}, the
papers whose citations we attempt to correctly predict. For each root paper we
attempted to retrieve all \textit{reference papers}, or papers listed in the
reference section of the root paper. For each reference paper, we retrieve
metadata of the paper--title and authors--and the abstract text. We prefer to
get the full text of a reference paper, but unfortunately we were unable to
retrieve these, and so we settled for paper abstracts. One of our main
objectives for the data, which we mostly satisfied, was to collect what we
refer to as \textit{complete papers}. A complete paper is a paper for which we
could retrieve metadata and abstracts for all reference papers.

In order to simplify our implementation, we maintain a particular structure of
the articles collected from PLoS. This structure dictates how the articles are
stored on disk (files with a particular format) and what data must be
possessed. This structure is further described in sections
\ref{sec:text_structure} and \ref{sec:dir_structure} below.
